---
title: "Homework 1"
author: Michelle Lui
output: github_document
---

This is my solution to HW1.  

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame from the specified elements. 

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```


Take the mean of each variable in my data frame. 
```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of numbers and logical but not character or factor. 


Convert each variable in my data frame into a numeric. 
```{r, results='hide'}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
For the logical vector, we get zeroes and ones when we convert to numeric because R interprets Trues and Falses as ones and zeroes, which makes sense since we were able to get a mean. 
For the character vector, we were not able to convert to numeric, and this make sense since
we couldn't get a mean. 
For the factor vector, we got the values 1, 2, and 3 when we converted to numeric because R is able to force factor vectors into numeric vectors; however we were not able to get a mean with a factor vector which is contradictory. 


```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

## Problem 2

Loading the penguins dataset. 
```{r}
data("penguins", package = "palmerpenguins")
```

Description of the penguins dataset.

The _Penguins_ dataset consists of `r ncol(penguins)` variables and `r nrow(penguins)` observations.
The names of the variables are `r names(penguins)`. There are `r nlevels(pull(penguins, species))` species in the dataset, which consist of `r levels(pull(penguins, species))`. There are `r nlevels(pull(penguins, island))` islands in the dataset, including `r levels(pull(penguins, island))`. The bill lengths of the penguins range from (`r range(pull(penguins, bill_length_mm), na.rm = TRUE)` mm) with a mean of `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)` mm. The bill depths of the penguins range from (`r range(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm), with a mean of `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm. The flipper length ranges from (`r range(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm), with a mean of `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. The body mass of the penguins range from (`r range(pull(penguins, body_mass_g), na.rm = TRUE)` grams), with a mean of `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`grams. 

Scatterplot of flipper length (mm) vs bill length (mm). 
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_scatterplot.pdf")
```



